The Proofs

### 2024-07-31 proofs/tex/subst-algo-lemmas.tex
prettify + minor edits

\lemmaSubstEqAlgVar*
\begin{proof}
  The proof is a simple structural induction on 
  $[[Γ; Ξ ⊢ uP]]$ and mutually, on $[[Γ; Ξ ⊢ uN]]$.
  Let us consider the shape of $[[uN]]$ (the cases of $[[uP]]$ are symmetric).
  \begin{caseof}
    \item $[[Γ; Ξ ⊢ α̂⁻]]$. Then $[[ [uσ1]α̂⁻ = [uσ2]α̂⁻ ]]$
      implies $[[uσ1|(uv α̂⁻) = uσ2|(uv α̂⁻)]]$ immediately.
    \item $[[Γ; Ξ ⊢ α⁻]]$. Then $[[uv α̂⁻ = ∅]]$, and
      $[[uσ1|(uv α̂⁻)  = uσ2|(uv α̂⁻)]]$ holds vacuously.
    \item $[[Γ; Ξ ⊢ ∀pas.uN]]$. Then we are proving that
      $[[ [uσ1]∀pas.uN = [uσ2]∀pas.uN ]]$ implies $[[uσ1|(uv ∀pas.uN) = uσ2|(uv ∀pas.uN)]]$.
      By definition of substitution and \ruleref{\ottdruleEOneForallLabel}, 
      $[[ [uσ1]uN = [uσ2]uN ]]$ implies $[[uσ1|uv uN = uσ2|uv uN]]$.
      Since $[[∀pas.uN]]$ is normalized, so is $[[Γ, pas; Ξ ⊢ uN]]$, 
      hence, the induction hypothesis is applicable and implies $[[uσ1|uv uN = uσ2|uv uN]]$,
      as required.
    \item $[[Γ; Ξ ⊢ uP → uN]]$. Then we are proving that
      $[[ [uσ1](uP → uN) = [uσ2](uP → uN) ]]$ implies $[[uσ1|(uv uP → uN) = uσ2|(uv uP → uN)]]$.
      By definition of substitution and congruence of equality, 
      $[[ [uσ1](uP → uN) = [uσ2](uP → uN) ]]$
      means $[[ [uσ1]uP = [uσ2]uP ]]$ and $[[ [uσ1]uN = [uσ2]uN ]]$.
      Notice that $[[uP]]$ and $[[uN]]$ are normalized since $[[uP → uN]]$ is normalized, 
      and well-formed in the same contexts.
      This way, by the induction hypothesis, 
      $[[uσ1|(uv uP) = uσ2|(uv uP)]]$ and $[[uσ1|(uv uN) = uσ2|(uv uN)]]$,
      which since $[[uv (uP → uN) = uv uP ∪ uv uN]]$ implies
      $[[uσ1|(uv uP → uN) = uσ2|(uv uP → uN)]]$.
    \item $[[Γ; Ξ ⊢ ↑uP]]$. The proof is similar to the previous case:
      we apply congruence of substitution, equality, and normalization,
      then the induction hypothesis, and then the fact that $[[uv (↑uP) = uv uP]]$.
  \end{caseof}
\end{proof}

\corollarySubstEquivAlgVar*
\begin{proof}
  First, let us normalize the types and the substitutions, and show that
  the given equivalences and well-formedness properties are preserved. 
  $[[Γ; Ξ ⊢ uP]]$ implies $[[Γ; Ξ ⊢ nf(uP)]]$ by \cref{corollary:wf-nf-algo}.
  $[[Θ ⊢ [uσ1]uP ≈ [uσ2]uP]]$ implies $[[ nf([uσ1]uP) = nf([uσ2]uP)]]$ by 
  \cref{lemma:subt-equiv-algorithmization}.
  Then $[[ nf([uσ1]uP) = nf([uσ2]uP)]]$ implies 
  $[[ [nf(uσ1)]nf(uP) = [nf(uσ2)]nf(uP)]]$ by \cref{lemma:norm-subst-distr}.
  Notice that by \cref{corollary:norm-subst-sig-algo}
  $[[Θ ⊢ uσi : Ξ]]$ implies $[[Θ ⊢ nf(uσi) : Ξ]]$.

  This way, by \cref{lemma:subst-eq-algovar}, 
  $[[Θ ⊢ [uσ1]uP ≈ [uσ2]uP]]$ implies 
  $[[nf(uσ1)|(uv nf(uP)) = nf(uσ2)|(uv nf(uP))]]$.
  Then by \cref{lemma:uv-nf}, 
  $[[nf(uσ1)|(uv uP) = nf(uσ2)|(uv uP)]]$,
  and by \cref{corollary:subst-subt-equiv-algorithmization},
  $[[Θ ⊢ uσ1 ≈ uσ2 : uv uP]]$.

  Symmetrically, 
  $[[Θ ⊢ [uσ1]uN ≈ [uσ2]uN]]$ implies 
  $[[Θ ⊢ uσ1 ≈ uσ2 : uv uN]]$.
\end{proof}

>>>>

\lemmaSubstEqAlgVar*
\begin{proof}
  The proof is a simple structural induction on 
  $[[Γ; Ξ ⊢ uP]]$ and mutually, on $[[Γ; Ξ ⊢ uN]]$.
  Let us consider the shape of $[[uN]]$ (the cases of $[[uP]]$ are symmetric).
  \begin{caseof}
    \item $[[Γ; Ξ ⊢ α̂⁻]]$. Then $[[ [uσ1]α̂⁻ = [uσ2]α̂⁻ ]]$
      implies $[[uσ1|(uv α̂⁻) = uσ2|(uv α̂⁻)]]$ immediately.
    \item $[[Γ; Ξ ⊢ α⁻]]$. Then $[[uv α̂⁻ = ∅]]$, and
      $[[uσ1|(uv α̂⁻)  = uσ2|(uv α̂⁻)]]$ holds vacuously.
    \item $[[Γ; Ξ ⊢ ∀pas.uN]]$. Then we are proving that
      $[[ [uσ1]∀pas.uN = [uσ2]∀pas.uN ]]$ implies $[[uσ1|(uv ∀pas.uN) = uσ2|(uv ∀pas.uN)]]$.
      By definition of substitution and \ruleref{\ottdruleEOneForallLabel}, 
      $[[ [uσ1]uN = [uσ2]uN ]]$ implies $[[uσ1|uv uN = uσ2|uv uN]]$.
      Since $[[∀pas.uN]]$ is normalized, so is $[[Γ, pas; Ξ ⊢ uN]]$, 
      hence, the induction hypothesis is applicable and implies $[[uσ1|uv uN = uσ2|uv uN]]$,
      as required.
    \item $[[Γ; Ξ ⊢ uP → uN]]$. Then we are proving that
      $[[ [uσ1](uP → uN) = [uσ2](uP → uN) ]]$ implies $[[uσ1|(uv uP → uN) = uσ2|(uv uP → uN)]]$.
      By definition of substitution and congruence of equality, 
      $[[ [uσ1](uP → uN) = [uσ2](uP → uN) ]]$
      means $[[ [uσ1]uP = [uσ2]uP ]]$ and $[[ [uσ1]uN = [uσ2]uN ]]$.
      Notice that $[[uP]]$ and $[[uN]]$ are normalized since $[[uP → uN]]$ is normalized, 
      and well-formed in the same contexts.
      This way, by the induction hypothesis, 
      $[[uσ1|(uv uP) = uσ2|(uv uP)]]$ and $[[uσ1|(uv uN) = uσ2|(uv uN)]]$,
      which since $[[uv uP → uN = uv uP ∪ uv uN]]$ implies
      $[[uσ1|(uv uP → uN) = uσ2|(uv uP → uN)]]$.
    \item $[[Γ; Ξ ⊢ ↑uP]]$. The proof is similar to the previous case:
      we apply congruence of substitution, equality, and normalization,
      then the induction hypothesis, and then the fact that $[[uv ↑uP = uv uP]]$.
  \end{caseof}
\end{proof}

\corollarySubstEquivAlgVar*
\begin{proof}
  First, let us normalize the types and the substitutions, and show that
  the given equivalences and well-formedness properties are preserved. 
  $[[Γ; Ξ ⊢ uP]]$ implies $[[Γ; Ξ ⊢ nf(uP)]]$ by \cref{corollary:wf-nf-algo}.
  $[[Γ ⊢ [uσ1]uP ≈ [uσ2]uP]]$ implies $[[ nf([uσ1]uP) = nf([uσ2]uP)]]$ by 
  \cref{lemma:subt-equiv-algorithmization}.
  Then $[[ nf([uσ1]uP) = nf([uσ2]uP)]]$ implies 
  $[[ [nf(uσ1)]nf(uP) = [nf(uσ2)]nf(uP)]]$ by \cref{lemma:norm-subst-distr}.
  Notice that by \cref{corollary:norm-subst-sig-algo}
  $[[Θ ⊢ uσi : Ξ]]$ implies $[[Θ ⊢ nf(uσi) : Ξ]]$.

  This way, by \cref{lemma:subst-eq-algovar}, 
  $[[Γ ⊢ [uσ1]uP ≈ [uσ2]uP]]$ implies 
  $[[nf(uσ1)|(uv nf(uP)) = nf(uσ2)|(uv nf(uP))]]$.
  Then by \cref{lemma:uv-nf}, 
  $[[nf(uσ1)|(uv uP) = nf(uσ2)|(uv uP)]]$,
  and by \cref{corollary:subst-subt-equiv-algorithmization},
  $[[Θ ⊢ uσ1 ≈ uσ2 : uv uP]]$.

  Symmetrically, 
  $[[Γ ⊢ [uσ1]uN ≈ [uσ2]uN]]$ implies 
  $[[Θ ⊢ uσ1 ≈ uσ2 : uv uN]]$.
\end{proof}

### 2024-07-31 proofs/tex/unification-lemmas.tex
prettify + minor edits

        \item $[[uN]] = [[α⁻]]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv(α⁻)]]$ such that $[[ [uσ]α⁻ = iM ]]$.
            Since $[[uv(α⁻) = ∅]]$, $[[ [us]α⁻ = iM ]]$ means $[[iM = α⁻]]$.

@@

        \item $[[uN]] = [[↑uP]]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv(uP)]]$ such that $[[ [uσ]↑uP = iM ]]$.
            The latter means $[[ ↑[uσ]uP = iM ]]$, i.e.
            $[[iM]] = [[↑iQ]]$ for some $[[iQ]]$ and $[[ [uσ]uP = iQ ]]$.

@@

        \item $[[uN]] = [[uP → uN']]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv(uP → uN')]]$ such that $[[ [uσ](uP → uN') = iM ]]$.
            The latter means $[[ [uσ]uP → [uσ]uN' = iM ]]$, i.e.
            $[[iM]] = [[iQ → iM']]$ for some $[[iQ]]$ and $[[iM']]$, 
            such that $[[ [uσ]uP = iQ ]]$ and $[[ [uσ]uN' = iM' ]]$.

            Let us show that the induction hypothesis is applicable to 
            $[[Θ ⊢ uσ|uv(uP) : uv(uP)]]$ and $[[ [uσ|uv(uP)]uP = iQ ]]$ 
            (the latter holds since $[[ [uσ|uv(uP)]uP = [uσ]uP ]]$ by \cref{lemma:subst-restr-uv}),
            \begin{itemize}
                \item $[[uP]]$ is normalized, since $[[uN]] = [[uP → uN']]$ is normalized
                \item $[[Γ ; dom(Θ) ⊢ uP]]$ follows from the inversion of $[[Γ ; dom(Θ) ⊢  uP → uN']]$,
                \item $[[Γ ⊢ iQ]]$.
            \end{itemize}
            Then by the induction hypothesis, $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC1]]$.
            Analogously, the induction hypothesis is applicable to $[[ [uσ|uv uN']uN' = iM' ]]$,
            and thus, $[[Γ ; Θ ⊨ uN' ≈u iM' ⫤ UC2]]$.

            To apply \ruleref{\ottdruleUArrowLabel} and infer the required
            $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$,
            it is left to show that $[[Θ ⊢ UC1 & UC2 = UC]]$.
            It holds by completeness of the unification constraint merge 
            (\cref{lemma:unif-merge-completeness})
            for $[[Θ ⊢ lift UC1 : uv uP]]$, 
                $[[Θ ⊢ lift UC2 : uv uN']]$ (which hold by soundness),
                and $[[Θ ⊢ uσ : uv(uP) ∪ uv(uN')]]$, 
                which holds since $[[uv(uP) ∪ uv(uN') = uv(uP → uN')]]$.
            Notice that by soundness, $[[Θ ⊢ uσ|uv(uP) : lift UC1]]$, 
            which implies $[[Θ ⊢ uσ : lift UC1]]$.
            Analogously, $[[Θ ⊢ uσ : lift UC2]]$.

        \item $[[uN]] = [[∀pas.uN']]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv(uN')]]$ such that $[[ [uσ]∀pas.uN' = iM ]]$.
            The latter means $[[ ∀pas.[uσ]uN' = iM ]]$, i.e.
            $[[iM]] = [[∀pas.iM']]$ for some $[[iM']]$ such that $[[ [uσ]uN' = iM' ]]$.

            Let us show that the induction hypothesis is applicable to $[[ [uσ]uN' = iM' ]]$.
            Notice that $[[uN']]$ is normalized, since $[[uN]] = [[∀pas.uN']]$ is normalized,
            $[[Γ,pas ; dom(Θ) ⊢ uN']]$ follows from inversion of $[[Γ ; dom(Θ) ⊢  ∀pas.uN']]$,
            $[[Γ,pas ⊢ iM']]$ follows from inversion of $[[Γ ⊢ ∀pas.iM']]$, and
            $[[Θ ⊢ uσ : uv(uN')]]$ by assumption.

>>>>

        \item $[[uN]] = [[α⁻]]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv α⁻]]$ such that $[[ [uσ]α⁻ = iM ]]$.
            Since $[[uv α⁻ = ∅]]$, $[[ [us]α⁻ = iM ]]$ means $[[iM = α⁻]]$.

@@

        \item $[[uN]] = [[↑uP]]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv uP]]$ such that $[[ [uσ]↑uP = iM ]]$.
            The latter means $[[ ↑[uσ]uP = iM ]]$, i.e.
            $[[iM]] = [[↑iQ]]$ for some $[[iQ]]$ and $[[ [uσ]uP = iQ ]]$.

@@

        \item $[[uN]] = [[uP → uN']]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv uP → uN']]$ such that $[[ [uσ](uP → uN') = iM ]]$.
            The latter means $[[ [uσ]uP → [uσ]uN' = iM ]]$, i.e.
            $[[iM]] = [[iQ → iM']]$ for some $[[iQ]]$ and $[[iM']]$, 
            such that $[[ [uσ]uP = iQ ]]$ and $[[ [uσ]uN' = iM' ]]$.

            Let us show that the induction hypothesis is applicable to 
            $[[Θ ⊢ uσ|uv uP : uv uP]]$ and $[[ [uσ|uv uP]uP = iQ ]]$ 
            (the latter holds since $[[ [uσ|uv uP]uP = [uσ]uP ]]$ by \cref{lemma:subst-restr-uv}),
            \begin{itemize}
                \item $[[uP]]$ is normalized, since $[[uN]] = [[uP → uN']]$ is normalized
                \item $[[Γ ; dom(Θ) ⊢ uP]]$ follows from the inversion of $[[Γ ; dom(Θ) ⊢  uP → uN']]$,
                \item $[[Γ ⊢ iQ]]$.
            \end{itemize}
            Then by the induction hypothesis, $[[Γ ; Θ ⊨ uP ≈u iQ ⫤ UC1]]$.
            Analogously, the induction hypothesis is applicable to $[[ [uσ|uv uN']uN' = iM' ]]$,
            and thus, $[[Γ ; Θ ⊨ uN' ≈u iM' ⫤ UC2]]$.

            To apply \ruleref{\ottdruleUArrowLabel} and infer the required
            $[[Γ ; Θ ⊨ uN ≈u iM ⫤ UC]]$,
            it is left to show that $[[Θ ⊢ UC1 & UC2 = UC]]$.
            It holds by completeness of the unification constraint merge 
            (\cref{lemma:unif-merge-completeness})
            for $[[Θ ⊢ lift UC1 : uv uP]]$, 
                $[[Θ ⊢ lift UC2 : uv uN']]$ (which hold by soundness),
                and $[[Θ ⊢ uσ : uv uP ∪ uv uN']]$, 
                which holds since $[[uv uP ∪ uv uN' = uv uP → uN']]$.
            Notice that by soundness, $[[Θ ⊢ uσ|uv uP : lift UC1]]$, 
            which implies $[[Θ ⊢ uσ : lift UC1]]$.
            Analogously, $[[Θ ⊢ uσ : lift UC2]]$.

        \item $[[uN]] = [[∀pas.uN']]$\\
            Let us take an arbitrary $[[Θ ⊢ uσ : uv uN']]$ such that $[[ [uσ]∀pas.uN' = iM ]]$.
            The latter means $[[ ∀pas.[uσ]uN' = iM ]]$, i.e.
            $[[iM]] = [[∀pas.iM']]$ for some $[[iM']]$ such that $[[ [uσ]uN' = iM' ]]$.

            Let us show that the induction hypothesis is applicable to $[[ [uσ]uN' = iM' ]]$.
            Notice that $[[uN']]$ is normalized, since $[[uN]] = [[∀pas.uN']]$ is normalized,
            $[[Γ,pas ; dom(Θ) ⊢ uN']]$ follows from inversion of $[[Γ ; dom(Θ) ⊢  ∀pas.uN']]$,
            $[[Γ,pas ⊢ iM']]$ follows from inversion of $[[Γ ⊢ ∀pas.iM']]$, and
            $[[Θ ⊢ uσ : uv uN']]$ by assumption.

### 2024-07-31 proofs/tex/upgrade-lemmas.tex
prettify + minor edits

\lemmaUpgradeSoundness*
\begin{lemma}[Soundness of Upgrade]\label{lemma:upgrade-soundness}
    Assuming $[[iP]]$ is well-formed in $[[Γ = Δ, pnas]]$,
    if $[[upgrade Γ ⊢ iP to Δ = iQ]]$
    then
    \begin{enumerate}
        \item $[[Δ ⊢ iQ]]$
        \item $[[Γ ⊢ iQ ≥ iP]]$
    \end{enumerate}
\end{lemma}
\begin{proof}
    By inversion, $[[upgrade Γ ⊢ iP to Δ = iQ]]$ means that 
    for fresh $[[pnbs]]$ and $[[pncs]]$,
    $[[Δ, pnbs, pncs ⊨ [pnbs/pnas]iP ∨ [pncs/pnas]iP = iQ]]$.
    Then by the soundness of the least upper bound (\cref{lemma:lub-soundness}),
    \begin{enumerate}
        \item $[[Δ, pnbs, pncs ⊢ iQ]]$, 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pnbs/pnas]iP]]$, and 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pncs/pnas]iP]]$.
    \end{enumerate}
    \begin{align*}
        [[fv iQ]] &\subseteq [[fv [pnbs/pnas]iP ∩ fv [pncs/pnas]iP]]
                  &&\text{since by \cref{lemma:fv-propagation}, 
                         $[[fv iQ ⊆ fv [pnbs/pnas]iP]]$}\\
                  & &&  \text{and $[[fv iQ ⊆ fv [pncs/pnas]iP]]$}\\
                  &\subseteq [[ ((fv iP \ {pnas}) ∪ {pnbs}) ∩ ((fv iP \ {pnas}) ∪ {pncs})]]\\
                  &= [[ (fv iP \ {pnas}) ∩ (fv iP \ {pnas}) ]]
                  &&\text{since $[[pnbs]]$ and $[[pncs]]$ are fresh}\\
                  &= [[ fv iP \ {pnas} ]]\\
                  &\subseteq [[ Γ \ {pnas} ]]
                  &&\text{since $[[iP]]$ is well-formed in $[[Γ]]$}\\
                  &\subseteq [[ {Δ} ]]\\
    \end{align*}
    This way, by \cref{lemma:wf-ctxt-equiv}, $[[Δ ⊢ iQ]]$.

>>>>

\lemmaUpgradeSoundness*
\begin{lemma}[Soundness of Upgrade]\label{lemma:upgrade-soundness}
    Assuming $[[iP]]$ is well-formed in $[[Γ = Δ, pnas]]$,
    if $[[upgrade Γ ⊢ iP to Δ = iQ]]$
    then
    \begin{enumerate}
        \item $[[Δ ⊢ iQ]]$
        \item $[[Γ ⊢ iQ ≥ iP]]$
    \end{enumerate}
\end{lemma}
\begin{proof}
    By inversion, $[[upgrade Γ ⊢ iP to Δ = iQ]]$ means that 
    for fresh $[[pnbs]]$ and $[[pncs]]$,
    $[[Δ, pnbs, pncs ⊨ [pnbs/pnas]iP ∨ [pncs/pnas]iP = iQ]]$.
    Then by the soundness of the least upper bound (\cref{lemma:lub-soundness}),
    \begin{enumerate}
        \item $[[Δ, pnbs, pncs ⊢ iQ]]$, 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pnbs/pnas]iP]]$, and 
        \item $[[Δ, pnbs, pncs ⊢ iQ ≥ [pncs/pnas]iP]]$.
    \end{enumerate}
    \begin{align*}
        [[fv iQ]] &\subseteq [[fv [pnbs/pnas]iP ∩ fv [pncs/pnas]iP]]
                  &&\text{by \cref{lemma:fv-propagation}, 
                         $[[fv iQ ⊆ fv [pnbs/pnas]iP]]$}\\
                  & &&  \text{and $[[fv iQ ⊆ fv [pncs/pnas]iP]]$}\\
                  &\subseteq [[ ((fv iP \ {pnas}) ∪ {pnbs}) ∩ ((fv iP \ {pnas}) ∪ {pncs})]]\\
                  &= [[ (fv iP \ {pnas}) ∩ (fv iP \ {pnas}) ]]
                  &&\text{since $[[pnbs]]$ and $[[pncs]]$ are fresh}\\
                  &= [[ fv iP \ {pnas} ]]\\
                  &\subseteq [[ Γ \ {pnas} ]]
                  &&\text{since $[[iP]]$ is well-formed in $[[Γ]]$}\\
                  &\subseteq [[ {Δ} ]]\\
    \end{align*}
    This way, by \cref{lemma:wf-ctxt-equiv}, $[[Δ ⊢ iQ]]$.

### 2024-07-31 proofs/tex/wf-algo-lemmas.tex
prettify + minor edits

\lemmaWfAlgoSoundness*
\begin{proof}
  The proof is analogous to \cref{lemma:wf-soundness}.
  The additional base case is when $[[Γ ; Ξ ⊢ uP]]$ is derived by \ruleref{\ottdruleWFATPUVarLabel},
  and the symmetric negative case.
  In this case, $[[uP]] = [[α̂⁺]]$, and $[[uv(uP)]] = [[{α̂⁺} ⊆ Ξ]]$ by inversion; $[[fv(uP)]] = [[∅ ⊆ Γ]]$ vacuously.
\end{proof}

@@

\corollaryWfWeakeningAlgo*
\begin{proof}
  By \cref{lemma:wf-algo-soundness},
  $[[Γ1; Ξ1 ⊢ uP]]$ implies $[[fv(uP) ⊆ Γ1 ⊆ Γ2]]$
  and $[[uv(uP) ⊆ Ξ1 ⊆ Ξ2]]$,
  and thus, $[[fv(uP)]] = [[fv(uP) ∩ Γ1]] = [[fv(uP) ∩ Γ2]]$, 
  and $[[uv(uP)]] = [[uv(uP) ∩ Ξ1]] = [[uv(uP) ∩ Ξ2]]$.
  Then by \cref{lemma:wf-algo-ctxt-equiv}, $[[Γ2; Ξ2 ⊢ uP]]$. 
  The negative case is symmetric.
\end{proof}

>>>>

\lemmaWfAlgoSoundness*
\begin{proof}
  The proof is analogous to \cref{lemma:wf-soundness}.
  The additional base case is when $[[Γ ; Ξ ⊢ uP]]$ is derived by \ruleref{\ottdruleWFATPUVarLabel},
  and the symmetric negative case.
  In this case, $[[uP]] = [[α̂⁺]]$, and $[[uv uP]] = [[{α̂⁺} ⊆ Ξ]]$ by inversion; $[[fv(uP)]] = [[∅ ⊆ Γ]]$ vacuously.
\end{proof}

@@

\corollaryWfWeakeningAlgo*
\begin{proof}
  By \cref{lemma:wf-algo-soundness},
  $[[Γ1; Ξ1 ⊢ uP]]$ implies $[[fv(uP) ⊆ Γ1 ⊆ Γ2]]$
  and $[[uv uP ⊆ Ξ1 ⊆ Ξ2]]$,
  and thus, $[[fv(uP)]] = [[fv(uP) ∩ Γ1]] = [[fv(uP) ∩ Γ2]]$, 
  and $[[uv uP]] = [[uv uP ∩ Ξ1]] = [[uv uP ∩ Ξ2]]$.
  Then by \cref{lemma:wf-algo-ctxt-equiv}, $[[Γ2; Ξ2 ⊢ uP]]$. 
  The negative case is symmetric.
\end{proof}
